Robust Bayesian Analysis of Causal Inference Problems

### 2022-11-01 JASA-template.tex
dss addition

\subsection{Co-variate selection}
For the co-variate selection, we look into the posterior expectation of $\pi_j$. 
We consider the $j$-th group to be active, if
\begin{align}
    \lexp (\pi_j\mid W)\coloneqq \inf_{q_j\in \mathcal{P}_j} \text{E}(\pi_j\mid W) > 1/2
\end{align}
and inactive, if
\begin{align}
    \uexp(\pi_j\mid W) \coloneqq \sup_{q_j\in \mathcal{P}_j} \text{E}(\pi_j\mid W)< 1/2.
\end{align}
We consider the rest to be indecisive.

This way, we get a robust group selection routine. However, this type of variable 
selection includes both treatment and outcome effects at the same time. This may not be the
case in some cases especially when either treatment effect or the outcome effect is zero or
weak. To deal with such problems, we suggest the following ad-hoc method to obtain 
adjusted sparse estimate of the zero effect in a selected group.
Let $\mathcal{S}$ denote the set of active co-variates present in the model. That is,
\begin{equation}
    \mathcal{S}\coloneqq
    \left\{j : \lexp(\pi_j\mid W) > 1/2\right\}.
\end{equation}
Let $\hat{\beta}_{\mathcal{S}}(q_{\mathcal{S}})$ be the posterior means of the regression
coefficients for the non-zero outcome effects and
$\hat{\gamma}_{\mathcal{S}}(q_{\mathcal{S}})$ be the posterior means of the regression
coefficients for the non-zero treatment effects. We apply the 
``decoupled shrinkage and selection'' method proposed by \citet{hahn2015}, to obtain
the sparse estimate. To do so, we solve the following adaptive LASSO-type \cite{Zou2006}
problems

\begin{align}
    \hat{\beta}^*_{\mathcal{S}}(q_{\mathcal{S}}) &= 
    \arg\min_{\beta_{\mathcal{S}}} \frac{1}{n}\|\x_{\mathcal{S}}\hat{\beta}_{\mathcal{S}}(q_{\mathcal{S}})
    - \x_{\mathcal{S}} \beta_{\mathcal{S}}\|_2^2 + \lambda_1\sum_{j\in\mathcal{S}} 
    \frac{|\beta_j|}{|\hat{\beta}_j(q_j)|}
\end{align}
and
\begin{align}
    \hat{\gamma}^*_{\mathcal{S}}(q_{\mathcal{S}}) &= 
    \arg\min_{\gamma_{\mathcal{S}}} \frac{1}{n}\|\x_{\mathcal{S}}\hat{\gamma}_{\mathcal{S}}(q_{\mathcal{S}})
    - \x_{\mathcal{S}} \gamma_{\mathcal{S}}\|_2^2 + \lambda_1\sum_{j\in\mathcal{S}} 
    \frac{|\gamma_j|}{|\hat{\gamma}_j(q_j)|}
\end{align}
where $q_{\mathcal{S}}\in \mathcal{P}_{\mathcal{S}}$.

\subsection{Robust Bayesian Analysis}
We perform our
robust Bayesian analysis on $q\coloneqq(q_1$, \dots, $q_p)\in\mathcal{P}$, where
\begin{equation}
\mathcal{P} \coloneqq \mathcal{P}_1\times\cdots\times\mathcal{P}_p\subseteq \left(0, 1\right)^{p}.
\end{equation}

>>>>

\subsection{Variable selection and coefficient adjustment}
For the co-variate selection, we look into the posterior expectation of $\pi_j$. 
We consider the $j$-th predictor to be removed from both the
treatment and outcome model, if
\begin{align}
    \lexp (\pi_j\mid W)\coloneqq \inf_{q_j\in \mathcal{P}_j} \text{E}(\pi_j\mid W) > 1/2.
\end{align}

For the rest of the variables, some of them will be present
in the model as confounders and some will only be associated with
either the treatment. Let $\mathcal{S}$ denote the set of
predictors such that,
\begin{equation}
    \mathcal{S}\coloneqq
    \left\{j : \lexp(\pi_j\mid W) < 1/2\right\}.
\end{equation}
That is the set that contains all the variables which are not
removed from both treatment and outcome model. Now, for
each fixed value of $q$,
let $\hat{\beta}_{\mathcal{S}}(q_{\mathcal{S}})$ be the posterior means of the regression coefficients of the outcome model with respect to
the predictors that belong to $\mathcal{S}$. Similarly,
$\hat{\gamma}_{\mathcal{S}}(q_{\mathcal{S}})$ be the posterior means of the regression
coefficients for the treatment effects. Since, we use a continuous type
selection prior, these regression coefficients are non-zero in nature.
Therefore, to adjust the sparsity, we apply the 
``decoupled shrinkage and selection'' method proposed by \citet{hahn2015}. To do so, we solve the following adaptive LASSO-type \cite{Zou2006}
problems

\begin{align}
    \hat{\beta}^*_{\mathcal{S}}(q) &= 
    \arg\min_{\beta_{\mathcal{S}}} \frac{1}{n}\|X_{\mathcal{S}}\hat{\beta}_{\mathcal{S}}(q)
    - X_{\mathcal{S}} \beta_{\mathcal{S}}\|_2^2 + \lambda\sum_{j\in\mathcal{S}} 
    \frac{|\beta_j|}{|\hat{\beta}_j(q_j)|}
\end{align}
and
\begin{align}
    \hat{\gamma}^*_{\mathcal{S}}(q) &= 
    \arg\min_{\gamma_{\mathcal{S}}} \frac{1}{n}\|X_{\mathcal{S}}\hat{\gamma}_{\mathcal{S}}(q)
    - X_{\mathcal{S}} \gamma_{\mathcal{S}}\|_2^2 + \lambda\sum_{j\in\mathcal{S}} 
    \frac{|\gamma_j|}{|\hat{\gamma}_j(q_j)|}
\end{align}
where $q_{j}\in \mathcal{P}_{j}$ for all $j\in\mathcal{S}$.

\iffalse
\subsection{Causal effect adjustment} The DSS method explained
above give us adjusted coefficient estimates for the treatment
and outcome model. However, as result the causal effect estimate
remains the same and modelling with such adjusted sparse effect 
will contribute to the prediction error. Therefore, we need to 
adjust the causal effect estimate as well. We do that in three steps
similar to double residual regression procedure as suggested by
\citet{robinson1988}.

First we compute the predicted values of $Y$ with respect to
the adjusted regression coefficients so that,
\begin{equation}
\hat{Y}(q) 
= \hat{\beta}_0(q) + X_{\mathcal{S}}\hat{\beta}^*_{\mathcal{S}}(q)
\end{equation}
and the values of $T$ with respect to the adjusted
regression coefficients so that
\begin{equation}
\hat{T}(q) 
= \Phi\left(\hat{\gamma}_0(q) + X_{\mathcal{S}}\hat{\gamma}^*_{\mathcal{S}}(q)\right).
\end{equation}
Then we estimate the adjusted causal effect using the following linear
model
\begin{equation}
\left(Y-\hat{Y}(q)\right) = \left(T - \hat{T}(q)\right)\beta_{T} + \epsilon^*_i.
\end{equation}
That is 
\begin{equation}
\beta_{T}^* = \left(\left(T - \hat{T}(q)\right)^T\left(T - \hat{T}(q)\right)\right)^{-1}\left(T - \hat{T}(q)\right)^T\left(Y-\hat{Y}(q)\right)
\end{equation}

\fi
\subsection{Robust Bayesian Analysis}
We perform our
robust Bayesian analysis on $q\coloneqq(q_1$, \dots, $q_p)\in\mathcal{P}$, where
\begin{equation}
\mathcal{P} \coloneqq \mathcal{P}_1\times\cdots\times\mathcal{P}_p\subseteq \left(0, 1\right)^{p}.
\end{equation}
